Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 PandaEvolution.tex
Negative spaces fixing
Attempting the backflip, careful with faceplants...

The upcoming LHC Run 3 will require more resources than the Worldwide LHC
Computing Grid (WLCG) can provide. Currently, PanDA WMS uses more than 300,000
cores at over 100 Grid sites, with a peak performance of 0.3 petaFLOPS. This
capacity will be sufficient for the planned analysis and data processing, but it
will be insufficient for the Monte Carlo production workflow and any extra
activity. To alleviate these challenges, ATLAS is engaged in a program to expand
the current computing model to include additional resources such as the
opportunistic use of supercomputers.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_broker_architecture.pdf}
    \caption{PanDA Broker architecture as deployed on Titan. Numbers indicates
    the execution process of a detector simulation job, part of the production
    ATLAS MC workflow.}
\label{fig:panda_broker}
\end{figure}

>>>>

The upcoming LHC Run 3 will require more resources than the Worldwide LHC
Computing Grid (WLCG) can provide. Currently, PanDA WMS uses more than 300,000
cores at over 100 Grid sites, with a peak performance of 0.3 petaFLOPS. This
capacity will be sufficient for the planned analysis and data processing, but it
will be insufficient for the Monte Carlo production workflow and any extra
activity. To alleviate these challenges, ATLAS is expanding the current
computing model to include additional resources such as the opportunistic use of
supercomputers.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_broker_architecture.pdf}
    \vspace{-0.3in}
    \caption{PanDA Broker architecture as deployed on Titan. Numbers indicates
    the execution process of a detector simulation job, part of the production
    ATLAS MC workflow.}
\label{fig:panda_broker}
\end{figure}

### 2017-04-04 overall.tex
Attempting the backflip, careful with faceplants...

We evaluate the efficiency, scalability and reliability of the deployment of
PanDA WMS on Titan by characterizing the behavior of both PanDA Broker and
AthenaMP. All the measurements were performed between January 2016 and February
2017, hereafter called `experiment time window'.

>>>>

We evaluate the efficiency, scalability and reliability of the deployment of
PanDA WMS on Titan by characterizing the behavior of both PanDA Broker and
AthenaMP. We discuss challenges and limitations of our approach at multiple
levels arising from the specifics of workload, middleware and methods. All the
measurements were performed between January 2016 and February 2017, hereafter
called ‘experiment time window
